\chapter*{Acknowledgments}

I want to thank Prof. Dr. Roger Wattenhofer for admitting me into his group and allowing me to work almost entirely on Bitcoin. When I applied to join his group, I was not his typical Ph.D candidate; but Roger took a chance on me and I am grateful for that. Roger also gave me a small platform as the coordinator of the Blockchain group meetings, and helped me expand my research horizons. Roger also understands the libertarian appeal of Bitcoin - which mattered the most to me. In Roger, I found a kindred spirit. 

I want to thank Prof. Dr. Majid Khabbazian for collaborating with me on 3 of my papers. Majid is brimming with ideas, and it was a privilege to be a part of his thinking process once in a while.

I want to thank my ``students''. Torgin, for official and unofficial discussions on blockchains. Daniel, for reversing roles and being my manager at BTCS and hooking me on to trail running. 

I want to thank DISCO members and alumni. Christian Decker, who told me back in 2014 that he was doing a Ph.D on Bitcoin with Roger and made me go ``hmm...''. Darya, for being my first office-mate and showing me the ropes here at ETH. Roland, for helping me with the scariest speech of my life. Zeta, for showing me how academic research is done. Ard, for answering all my Zero Knowledge questions patiently. Yann, for being the backstop that saved my a** more than once. Kobi, for asking the provocative questions. Ye, for a different perspective on blockchains. And the rest of the DISCO group, for graciously accepting my early-lunch shenanigans and still including me in other activities.

The folks at BTCS were gracious hosts during my internship: esp. Robin. And Arthur, who surprised me more than once.

My parents - Anuradha and Bhaskara Rao; and my sister - Banumathy: They made me curious about how the world works and equipped me with tools to explore it. This Ph.D would not have been possible if it weren't for my wife Kriti Puniyani. She is my best friend, partner, and sounding-board. Thanks for helping me keep it real.

Finally: Satoshi Nakamoto and the cypherpunks who came before and after Satoshi. Thanks for giving me a cause \cite{bitcoin_whitepaper} to get behind.

\section*{Collaborations and Contributions}

\newcommand\chapterlistheader[1]{~\\ \noindent\textbf{\mbox{#1}}}

This dissertation is based on the following papers:

\chapterlistheader{Chapter~\ref{chapter:bribing}} is based on the publication \emph{Timelocked Bribing}~\cite{timelocked_bribing}. Co-authors are Majid Khabbazian and Roger Wattenhofer.

\chapterlistheader{Chapter~\ref{chapter:swaps}} is based on the publication \emph{Grief-free Atomic Swaps}~\cite{grief_free_atomic_swaps}. Co-authors are Majid Khabbazian and Roger Wattenhofer.


\chapterlistheader{Chapter~\ref{chapter:outpost}} is based on the publication \emph{Outpost: A responsive lightweight watchtower}~\cite{outpost}. Co-authors are Majid Khabbazian and Roger Wattenhofer.

\chapterlistheader{Chapter~\ref{chapter:oracles}} is based on the publication \emph{TWAP Oracle Attacks: Easier Done than Said?}~\cite{twap_oracle_attacks}. Co-authors are Torgin Mackinga and Roger Wattenhofer.

\afterpage{\blankpage}